Leveraging Diversity to Find Bugs\\ in JavaScript Engines

### 2018-08-02 paper/paper.tex
cosmetic
pass on abstract and intro

%Should I Fuzz my Inputs or Improve my Tests? 
\title{Assessing the Reliability of JavaScript Engines by Leveraging Diversity}

@@

%% JavaScript (\js{}) is a popular programming language for the
%% web. Finding errors in JS runtime engines is an important problem.
\begin{abstract}
This paper assesses the impact of Differential Testing (DT) to find
functional bugs in JS engines. This is an important problem given the
importance of JS today. DT has shown successful in finding bugs in
compilers and runtimes, but has not been thoroughly explored in this
important domain. Our study \Fix{...}
\end{abstract}

\begin{IEEEkeywords}
...
\end{IEEEkeywords}

@@

JavaScript (\js{}) is today one of the most popular programming
languages for the web~\cite{business-insider,stackify}. The interest
of the community for the language encourages constant improvements in
its specification and implementations. It is natural to expect that
such improvements entails sensible changes in runtime engines. Even
small changes can have a large impact in practice. For example, in
October 2014 a new attribute added to Array objects caused a bug that
resulted in MS Outlook web not working under
Chrome~\cite{array-bug-chromium-issue4247,array-bug-discussion}. To
sum, finding bugs in JS engines is an important problem specially
because of the speed the specification evolves and the availability of
various public engines today~\cite{kangax}.

%% WHAT WE DID
This paper reports the results of a study we conducted to assess
reliability of existing JS engines by leveraging implementation
diversity in two orthogonal ways. The first method considered is
\emph{test transplantation}. This approach evaluates the effects that
running \js{} test files from a given engine have in detecting bugs in
other engines. The intuition is that when bugs are found in some
engine implementation a test case is created and added to the
regression suite. Those test inputs often check interesting corner
cases that could reveal bugs in different engine implementations. The
second method considered is \emph{cross-engine differential
  testing}. This method fuzzes existing inputs, using existing
techniques, and then compares the output produced by different engines
using a differential oracle. One possible cause of output discrepancy
is a bug. It is worth noting that Differential
Testing~\cite{Brumley-etal-ss07} (DT) has been applied in a variety of
contexts to find bugs in
software~\cite{Yang-etal-pldi11,Chen-etal-fse2015,Argyros-etla-ccs16,Chen-etal-pldi16,petsios-etal-sp2017,SivakornAPKJ17,Zhang:2017:ATD:3097368.3097448}. It
automates test generation in scenarios where multiple implementations
of a system exist. DT leverages the diversity across system's
implementations to detect anomalous behavior. For example, Mozilla
runs JS files--created with the grammar-based fuzzer
jsfunfuzz~\cite{jsfunfuzz}--against different configurations of their
SpiderMonkey engine~\cite{jsfunfuzz-mozilla-bug} to find discrepancies
across different configurations of the same build (\eg{}, enabling or
not eager JIT compilation). They use this technique since 2002 and
have been able to find over 270 bugs since
then~\cite{jsfunfuzz-at-mozilla}, including security bugs.  In
contrast, cross-engine differential testing--the technique used in
this work--checks correctness by comparing the output produced by
\emph{different engines} on a fuzzed
input~\cite{patra2016learning}. This approach is not popularized,
certainly because it is more challenging to fully automate--a number
of legitimate reasons exist, other than a bug, for a test execution to
manifest discrepancy (see Table~\ref{tab:false-positives}).

@@

\section{JavaScript}
\label{sec:es6-design}

JavaScript engines are virtual machines that parse source code and
compile it in bytecodes. These engines implement some version of
ECMAScript\footnote{The name JavaScript still prevails today,
  certainly for historical reasons.} (\es{}), which emerged with the
goal to standardize variants of the language, such as Netscape's
JavaScript and Microsoft's JScript. The \es{} specification is
regulated by Ecma International~\cite{es6-website} under the
TC39~\cite{tc39-github} technical committee.  Every year, a new
version of the \es{} specification is produced with new features and
minor fixes. The canonical spec today is
ES6~\cite{ecmas262-spec-repo,ecmas262-spec}. Features of these
versions and supporting engines are publicly available~\cite{kangax}.
In the following, we briefly describe different sources of
discrepancies that can emerge across different engine implementations
as results of the active changes in the \es{} specification.

%% \Mar{what is that exactly? can we cite? is that only spec or actually
%%   code as most of java.* libraries.}  \Igor{seems like an API. They
%%   define the language behavior; grammar; values to static variables;
%%   the methods for each "class"(Object)...  These irregularities
%%   appears on engine implementation, maybe an wrong if statement and so
%%   on.} \Mar{Igor, avoid general discussion like $\leftarrow$this. look for
%%   explanation in some forum/tutorial and explain **when** you
%%   undertand the JS ecosystem design and can explain with confidence.}

\subsection{Undefined (Implementation-Dependent) Behavior}
\label{sec:imp-dep-behavior}

The \es{} spec uses the label ``implementation-dependent'' to indicate
cases where each engine developer can decide how to implement some
aspect of a functionality. In these cases, execution may differ from
engine to engine. One of the reasons implementation-dependent behavior
exists is to enable compiler optimizations. For example, the
\mcodeid{for-in} loop does not clearly specify the iteration
order~\cite{so-forin-undefined,javascript-in-chrome} and different
engines capitalize on that~\cite{for-in-undefined}. As another
example, \Fix{...}

\Mar{explain what is an **acceptable** incompatibilities. cite example
bug reports.}
\Igor{For example, the latest version of ES specs~\cite{es6-spec} describes that
the function \CodeIn{Number.toPrecision(precision)}, in general,
if precision is defined the method returns a String 
containing the Number value represented either 
in decimal exponential notation or in decimal 
fixed notation~\cite{es6-toPrecision}. The Number object uses a 
property that the specification describes as approximately so when we use 
toPrecision with a bigger precision, the values of each engine may vary, this
could be considered as a case of incompatibility by engine
design.}\Mar{I don't understand the example very well and don't understand the
  relationship with HI/LO.}

@@

\begin{table}[h]
  \centering
  \caption{\label{tab:test262}Number of failures in Test262 over
    a 7-day period.}
  \begin{tabular}{crrrrrrr}
    \toprule
           & 1 & 2 & 3 & 4 & 5 & 6 & 7 \\
    \jsc{} & - & - & - & - & - & - & - \\
    \veight{} & - & - & - & - & - & - & - \\
    \chakra{} & - & - & - & - & - & - & - \\
    \smonkey{} & - & - & - & - & - & - & - \\
    \bottomrule 
  \end{tabular}
\end{table}

@@

\begin{table}[h]
  \centering
  \caption{\label{tab:cross-testing}Number of failures observed exchanging
  test suites.}
  \begin{tabular}{crrrr}
    \toprule
    test suite/engine & \jsc{} & \veight{} & \chakra{} & \smonkey{} \\
    \midrule
    \jsc{} & - & - & - & -  \\
    \veight{} & - & - & - & -  \\
%    \chakra{} & - & - & - & -  \\
    Mozilla & - & - & - & -  \\
    Duktape & - & - & - & -  \\
    JerryScript & - & - & - & -  \\
    JSI & - & - & - & -  \\
    Tiny-js & - & - & - & -  \\
    \bottomrule 
  \end{tabular}
\end{table}

>>>>

%Should I Fuzz my Inputs or Improve my Tests? 
\title{Leveraging Diversity to Find Bugs\\ in JavaScript Engines}

@@

%% JavaScript (\js{}) is a popular programming language for the
%% web. Finding errors in JS runtime engines is an important problem.
\begin{abstract}
JavaScript is a very popular programming language today. Checking
reliability of JavaScript engines is therefore an important
problem. This paper reports on a study to assess reliability of
JavaScript engines by leveraging the rich diversity of open-source
implementations. We explored two methods for that---test
transplantation and cross-engine differential testing. Test
transplatation evaluates the effects of running test suites of a given
engine in another engine. Cross-engine differential testing evaluates
the effects of fuzzing existing inputs and then comparing the output
produced by different engines with a differential oracle. Our results
indicate that \Fix{...}
\end{abstract}

\begin{IEEEkeywords}
JavaScript; Diversity; Software Testing
\end{IEEEkeywords}

@@

JavaScript (\js{}) is today one of the most popular programming
languages for the web~\cite{business-insider,stackify}. The interest
of the community for the language encourages constant improvements in
its specification and implementations. It is natural to expect that
such improvements entails sensible changes in runtime engines. Even
small changes can have a large impact in practice. For example, in
October 2014 a new attribute added to Array objects caused a bug that
resulted in MS Outlook web not working under
Chrome~\cite{array-bug-chromium-issue4247,array-bug-discussion}. Finding
bugs in JS engines is therefore an important problem. It is also
challenging because of the speed the specification
evolves~\cite{ecmas262-spec-repo} and the fact that the behavior of
various language elements is undefined~\cite{so-undefined-behavior}
(\ie{} left for the implementation to define).

%% WHAT WE DID
This paper reports the results of a study we conducted to assess
reliability of existing JS engines by leveraging implementation
diversity in two orthogonal ways. The first method considered is
\emph{test transplantation}. This method evaluates the effects that
running \js{} test files from a given engine have in detecting bugs in
other engines. The intuition is that when a bug is found in some
engine a test case is created and added to the regression suite. Those
test inputs often check interesting scenarios that could reveal bugs
in different engine implementations. The second method considered is
\emph{cross-engine differential testing}. This method fuzzes existing
inputs~\cite{fuzz-testing-history} and then compares the output
produced by different engines using a differential oracle. One
possible cause of output discrepancy is a bug. It is worth noting that
Differential Testing~\cite{Brumley-etal-ss07} (DT) has been applied in
a variety of contexts to find
bugs~\cite{Yang-etal-pldi11,Chen-etal-fse2015,Argyros-etla-ccs16,Chen-etal-pldi16,petsios-etal-sp2017,SivakornAPKJ17,Zhang:2017:ATD:3097368.3097448}. It
automates test generation in scenarios where multiple implementations
of a system exist. DT leverages the diversity across system's
implementations to detect anomalous behavior. For example, Mozilla
runs JS files--created with the grammar-based fuzzer
jsfunfuzz~\cite{jsfunfuzz}--against different configurations of their
SpiderMonkey engine~\cite{jsfunfuzz-mozilla-bug} to find discrepancies
across different configurations of the same build (\eg{}, enabling or
not eager JIT compilation). They use this technique since 2002 and
have been able to find over 270 bugs since
then~\cite{jsfunfuzz-at-mozilla}, including security bugs.  In
contrast, cross-engine differential testing--the technique used in
this work--checks functional correctness by comparing the output
produced by \emph{different engines} on a fuzzed
input~\cite{patra2016learning}. This approach has not been
popularized, certainly because it is more challenging to fully
automate--a number of legitimate reasons exist, other than a bug, for
a test execution to manifest discrepancy (see
Table~\ref{tab:false-positives}). This study quantifies human effort
to find these bugs using this method.

@@

\section{JavaScript}
\label{sec:es6-design}
\label{sec:imp-dep-behavior}

JavaScript engines are virtual machines that parse source code and
compile it in bytecodes. These engines implement some version of
ECMAScript\footnote{The name JavaScript still prevails today,
  certainly for historical reasons.} (\es{}), which emerged with the
goal to standardize variants of the language, such as Netscape's
JavaScript and Microsoft's JScript. The \es{} specification is
regulated by Ecma International~\cite{es6-website} under the
TC39~\cite{tc39-github} technical committee.  Every year, a new
version of the \es{} specification is produced with new features and
minor fixes. The canonical spec today is
ES6~\cite{ecmas262-spec-repo,ecmas262-spec}. Features of these
versions and supporting engines are publicly available~\cite{kangax}.

It is worth noting that undefined behavior makes differential testing
more challenging.

In the following, we briefly describe different sources of
discrepancies that can emerge across different engine implementations
as results of the active changes in the \es{} specification.

The \es{} spec uses the label ``implementation-dependent'' to indicate
cases where each engine developer can decide how to implement some
aspect of a functionality. In these cases, the behavior of some
language element may differ from engine to engine. One reason this
flexibility in the spec exists is to enable compiler
optimizations. For example, the \mcodeid{for-in} loop does not clearly
specify the iteration
order~\cite{so-forin-undefined,javascript-in-chrome} and different
engines capitalize on that~\cite{for-in-undefined}.  As another
example, the latest version of the \es{} specification states that if
the \mcodeid{Number.toPrecision()} function is called with more than
one argument, then the behavior is
implementation-dependent~\cite{es6-toPrecision}. Various other cases
like this exist in the specification.

\subsection{Undefined (Implementation-Dependent) Behavior}

%% \Mar{explain what is an **acceptable** incompatibilities. cite example
%% bug reports.}
%% \Igor{For example, the latest version of ES specs~\cite{es6-spec} describes that
%% the function \CodeIn{Number.toPrecision(precision)}, in general,
%% if precision is defined the method returns a String 
%% containing the Number value represented either 
%% in decimal exponential notation or in decimal 
%% fixed notation. The Number object uses a 
%% property that the specification describes as approximately so when we use 
%% toPrecision with a bigger precision, the values of each engine may vary, this
%% could be considered as a case of incompatibility by engine
%% design.}\Mar{I don't understand the example very well and don't understand the
%%   relationship with HI/LO.}

@@

\begin{table}[h]
  \centering
  \caption{\label{tab:test262}Number of failures in Test262 over
    a 7-day period.}
  \begin{tabular}{crrrrrrr}
    \toprule
    engine\textbackslash{}day& 1 & 2 & 3 & 4 & 5 & 6 & 7 \\
    \midrule
    \jsc{} & - & - & - & - & - & - & - \\
    \veight{} & - & - & - & - & - & - & - \\
    \chakra{} & - & - & - & - & - & - & - \\
    \smonkey{} & - & - & - & - & - & - & - \\
    \bottomrule 
  \end{tabular}
\end{table}

@@

\begin{table}[h]
  \centering
  \caption{\label{tab:cross-testing}Number of failures observed exchanging
  test suites.}
  \begin{tabular}{crrrr}
    \toprule
    test suite\textbackslash{}engine & \jsc{} & \veight{} & \smonkey{} & \chakra{}\\
    \midrule
    Versions (18.07) & 233941 & 6.9.448 & 62.0b9 & 1.10.1 \\
    \midrule
    \jsc{} & - & 11 & - & -  \\
    \veight{} & - & - & - & -  \\
%    \chakra{} & - & - & - & -  \\
    Mozilla & - & 333 & - & -  \\
    Duktape & - & 80 & - & -  \\
    JerryScript & - & 92 & - & -  \\
    JSI & - & 14 & - & -  \\
    Tiny-js & - & 11 & - & -  \\
    \midrule
    Versions (01.08) & 234485 & 7.0.126 & 62.0b13 & 1.10.1 \\
    \midrule
    \jsc{} & \Fix{10} & 11 & 107 & 157   \\
    \veight{} & 29 & \Fix{0} & 0 & 0  \\
%    \chakra{} & - & - & - & -  \\
    Mozilla & 741 & 286 & \Fix{178} & 476   \\
    Duktape & 238 & 80 & 202 & 85   \\
    JerryScript & 94 & 89 & 90 & 91   \\
    JSI & 35 & 14 & 14 & 14   \\
    Tiny-js & 11 & 11 & 11 & 11  \\
    \bottomrule 
  \end{tabular}
\end{table}
